---
title: "W_UP_01"
author: "Taylor Stohl"
date: "25 May 2021"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

The number of pushups for football players depend on their position. There are line and skill players; we want to use the numerical~cat
helper file.

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
basicCN <- ggplot(mydata,aes(x=position,y=pushups))
```
## Now add in boxplot


  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="line player vs. skill")
```

This boxplot shows the total number of pushups of players. Results are categorized by position on the football team.
It is apparent in this plot that skill players are able to do a significantly larger amount of pushups in 2 minutes than line players. The white boxes in the plot represent 50% of the people in each category. The lines that extend above the boxes is the most pushups anyone could do. This shows that 75% of the skill players are able to do more than any of the line players. You can see this by the two box displays.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->




```{r}
favstats(pushups~position,data=mydata)
```
This graph shows that the mean-value of pushups for line players is 17.2 and the skill players mean-value was about 50. In two minutes, skill players on average were able to do almost three times more push ups than the line players.


## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

 
```{r}
t.test(pushups~position,data=mydata)
```
The p-value is 0.000009421.The p-value is a such a small number that this result is unlikely to occur by chance.


# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The original question was what players on the football team did more pushups:line players or skill players. Using evidence gathered from the boxplots and the numerical results, it is clear that the skill players average number of pushups in 2 minutes was almost three times greater than the line players. 50:17 skill players to line players. We conclude that the skill players can do more pushups than the line players by acknowledging how tiny the p-value is.

